---
output:
    github_document
---

```{r,include=F}
library(mncolors)

#More information can be found in the vignette, including which palettes work best for those with impaired colour vision.
#```r
# load the mncolors vignette
#vignette("mncolors")
#```

```

# MN Color Palettes

Use the `mncolors` package to paint your data with colors from the [MN state brand style
guide](https://mn.gov/portal/brand/style-guide/colors/), and a
few color palettes inspired by local landscapes and animals, such as tree frogs and crayfish. 

Use the palettes with `ggplot2` or `plot` to give your charts some MN style.

## Install

To install `mncolors`:

``` r
# First install the 'remotes' package
install.packages("remotes")

library(remotes)

# Now you can install mncolors from github
remotes::install_github("MPCA-data/mncolors")

``
## The Palettes

There are currently 10: primary, corn, accent, extended, blue, green, gray, safety, treefrog, caryfish, and _trout (coming soon...)_.

```{r see_palettes, echo=F, fig.height=9}
library(mncolors)

par(mfrow=c(length(mn_palettes)/2, 2), lheight = 2, mar=rep(1, 4), adj = 0)

for (i in 1:length(mn_palettes)) viz_palette(mn_palettes[[i]], names(mn_palettes)[i])
```

<br>

**More specifically:**

```{r list_palettes}
mn_palettes
```



## Examples

In a ggplot use the MN palettes with the `scale_fill_mn()` and `scale_color_mn()` functions.

```{r}
library(mncolors)
library(ggplot2)

# Primary
ggplot(data = mpg) +   
   geom_point(aes(x = displ, y = hwy, color = class), size = 6, alpha = 0.7) +
   scale_color_mn(palette = "primary", reverse = TRUE)


# Extended
ggplot(data = mpg) +   
   geom_point(aes(x = displ, y = hwy, color = class), size = 6, alpha = 0.7) +
   scale_color_mn(palette = "extended")

# Accent
ggplot(diamonds) + 
  geom_bar(aes(x = cut, fill = clarity)) +
  scale_fill_mn(palette = "accent")

# Crayfish
ggplot(diamonds) + 
  geom_col(aes(y = mean(price), x = cut, fill = cut)) +
  scale_fill_mn(palette = "crayfish")

```


Alternatively, use`mncolors()` to feed MN colors to the default ggplot functions.

```{r}
library(ggplot2)
library(hexbin)

# Heat map
dat <- data.frame(x = rnorm(10000), y = rnorm(10000))

ggplot(dat, aes(x = x, y = y)) +
    geom_hex() + 
    coord_fixed() +
    scale_fill_gradientn(colors = mncolors(120, palette = "primary"))


```


## Lots of colors!

Enter any number you want to `mncolors()` to return a bucket of colors.
```{r, eval=T}
mncolors(10, "blue")
```


```{r, fig.height=3, echo=F}
#Use RColorBrewer code to demo the palettes
n = 10

image(
   1:n, 1, as.matrix(1:n),
   col = mncolors(n, palette = "blue"),
   xlab = "mncolors(blue)", ylab = "", xaxt = "n", yaxt = "n", bty = "n"
)
```


```{r, eval=F}
mncolors(100, "green")
```

```{r, fig.height=3, echo=F}
n = 100

image(
   1:n, 1, as.matrix(1:n),
   col = mncolors(n, palette = "green"),
   xlab = "mncolors(green)", ylab = "", xaxt = "n", yaxt = "n", bty = "n"
)
```



In this example we use the `accent` palette directly via the `colorRampPalette()` function for base plot folks. 

```{r}
## basic example code
pal <- colorRampPalette(mn_palettes[["accent"]])

image(volcano, col = pal(20))
```


